Parsing Tweets into Universal Dependencies

### 2017-12-03 paper.tex
when discussing non-syn tokens, merge @-mention in rt construction and rt marker.

\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$#1]}}
\newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
\newcommand{\yicomment}[1]{\textcolor{green}{[#1 ---\textsc{Yi}]}}
%\newcommand{\yjcomment}[1]{}
%\newcommand{\nascomment}[1]{}
%\newcommand{\yicomment}[1]{}

@@

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Using the extended guidelines \yicomment{including tokenization, POS tagging and parsing? (need to mention the annotation process/pipeline system not only consists parsing in abstract)}, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
labeled attachments. 
It is more than four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Using the new treebank,
we build a pipeline system to parse raw tweets into UD. To overcome the
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 transition-based parsers into a single one. Our
parser achieves an improvement of 2.6 in LAS over \nascomment{which
  comparison is this?}\yjcomment{my bad, it was fixed.} the baseline
and outperforms parsers that are state-of-the-art on other treebanks in both accuracy and speed.
\end{abstract}

@@

Based on these annotations, we designed a pipeline to parse 
raw tweets into universal dependencies. Our pipeline includes: a
bidirectional LSTM (bi-LSTM)\yicomment{need cite lstm/bi-lstm here?} tokenizer, a word cluster-enhanced POS
tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT} \yicomment{no need for parenthesis?}, and a stack LSTM parser
with character-based word representations
\cite{ballesteros-dyer-smith:2015:EMNLP}, which we refer to as our
``baseline'' parser.
To overcome the noise in our annotated data and achieve better performance
without sacrificing computational efficiency, we 
distill a 20-parser ensemble into a single greedy  parser 
\cite{DBLP:journals/corr/HintonVD15}.
We show further  that learning directly from the exploration of the ensemble parser
is more beneficial than learning from the gold standard ``oracle''
transition sequence. Experimental results show that an improvement of more
than 2.6 points \nascomment{again, not sure what this is quoting}\yjcomment{fixed} in LAS over the
baseline parser can be achieved with our distillation method and that \yicomment{delete `that'?} it outperforms
other state-of-the-art parsers in both accuracy and running speed.

The contributions of this paper include:
\begin{itemize}
\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
and created a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech \yicomment{POS} tagging, and labeled universal dependencies annotation.
We also characterize the difficulties of creating such annotation.

@@

Kong et al.'s rapid, small-scale annotation effort was heavily constrained.  It was
carried out mostly by nonnative speakers \yicomment{should not emphasize non-native speakers (v2 also built by non-native speakers), but emphasize annotators with only cursory training, no clear annotation guidelines, no consensus/agreement on controversial cases, allow annotators to underspecify part of the tree and allow multiple different trees for the same tweets}, in a very short amount of
time (a day).  Driven both by the style of the text they sought to annotate
and by exigency, some of their annotation conventions included:
\begin{itemize}
\item Allowing an annotator to exclude tokens from the dependency
  tree.  A clear criterion for exclusion was not given, but many
  tokens were excluded because they were deemed ``non-syntactic''\yicomment{(e.g. retweet sign, topical hashtags, ...)}.
\item Allowing an annotator to merge a multiword expression into a
  single node in the dependency tree, with no internal structure.
  Annotators were allowed to take the same step with noun phrases.
\item Allowing multiple roots, since a single tweet might contain more
  than one sentence.
\end{itemize}
These conventions were justified on the grounds of making the
annotation easier for non-experts, but they must be revisited in our
effort to apply UD to tweets.

@@

%In Fig.~\ref{ex1}, {\tt RT} {\tt @yijialiu}, {\tt \#ACL2017}, {\tt http://url} and {\tt th} are all tagged as X and {\tt :)} is tagged as SYM. 
%{\tt rn} is tagged as ADV.
%We should note that multiple tokens are actually included in a phrasal abbreviation, and we use one of their tags as the tag of the whole abbreviation according to their dependency relation or semantic priority.
%If there is a hierarchy in the abbreviation, we use the tag of the head word. In UD, ``Right'' is the dependent of ``now '' in the dependency of {\tt rn}, so we tag {\tt rn} as ADV. 
%Although there is no head word in {\tt im}, we think that the subject is usually more informative than the tense in many downstream tasks such as semantic role labelling, so we use the tag of ``I'', e.g. PROPN as the tag of {\tt im}.  
%In Fig.~\ref{ex2}, {\tt RT} and {\tt $\heart$} would be tagged as VERB, {\tt http://url} as X, {\tt \#Awesome} as ADJ, {\tt \#NAACL}, {\tt @zypandora} and {\tt @nlpnoah} as PROPN. One exception is that we tag URLs always as X regardless whether they are syntactic tokens. The reason is that we observed, in UD\_English, that the URLs are all tagged as X and we want to conform with the UD dataset, although we think it is not appropriate and should be changed to tags such as PROPN when they are treated as syntactic tokens.

Compared to the coarse-grained \yicomment{fine-grained?}POS tagging effort of
\newcite{gimpel-EtAl:2011:ACL-HLT2011}, our approach simplifies some
matters.  For example, if a token is not considered syntactic by UD
conventions, it gets an \emph{other} (\texttt{X}) tag (Gimpel et
al.~had more extensive conventions).  Other phenomena, like
abbreviations, are more complicated for us, as discussed above;
Gimpel et al.~used a single part of speech for such expressions.

@@

Another important difference follows from the difference in
tokenization.  As discussed in \S\ref{sec:tok-anno}, UD calls for more
aggressive tokenization than that used by 
\newcite{gimpel-EtAl:2011:ACL-HLT2011} \yicomment{YICOMMENT: should be OCONNOR's paper? TOKENIZATION?}. In particular, Gimpel et al.~\yicomment{SAME HERE} opted out of tokenizing
contractions and possessives, introducing new parts of speech
instead.\footnote{These tags only account for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

@@

\paragraph{Non-syntactic tokens.}  
\begin{table}
\centering
\begin{tabular}{lrr}
\multicolumn{2}{r}{syntactic (\%)} & non-syntactic (\%)\\ \hline
emoticons & 0.25 & 0.95 \\
RT & 0.14 & 2.49\\
hashtag & 1.02 & 1.24 \\
URL & 0.67 & 2.38 \\
truncated words & 0.00 & 0.49 \\
 \hline
 total & 2.08 & 7.55 \\
\end{tabular}
\caption{Proportions of non-syntactic tokens in our annotation. \yicomment{should add also retweet at-mentions}
These statistics are obtained on 140 character-limited tweets. \label{tbl:non-synt-prop}}
\end{table}

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& \textcolor{green}{\bf @coldplay} \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \& \tiny ADJ \& \tiny X \& \tiny PUNCT \\
		\end{deptext}
		\deproot{1}{root}
		\depedge[edge unit distance=1em]{1}{2}{discourse}
		\deproot{6}{root}
		\depedge[edge unit distance=1em]{6}{3}{discourse}
		\depedge[edge unit distance=1em]{3}{4}{discourse}
		\depedge[edge unit distance=1em]{3}{5}{punct}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.8em]{6}{10}{obl}
		\depedge[edge unit distance=1em]{10}{8}{case}
		\depedge[edge unit distance=1em]{10}{9}{det}
		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
		\depedge[edge unit distance=0.8em]{6}{12}{list}
		\deproot{13}{root}		
		\depedge[edge unit distance=0.8em]{13}{14}{discourse}
		\depedge[edge unit distance=0.8em]{13}{15}{punct}
	\end{dependency}
	\caption{An example tweet that contains non-syntactic tokens:
		\textcolor{red}{sentiment emoticon},
		\textcolor{orange}{retweet marker},
		\textcolor{green}{retweet at-mention},
		\textcolor{gray}{topical hashtag},
		\textcolor{blue}{referential URL}, and
		\textcolor{cyan}{truncated word}.
		This example tweet is a concatenation of three real tweets.
	}\label{fig:non-syn-toks}
\end{figure*}

@@

The major characteristic that distinguishes tweets from standard texts is that
a large proportion of tokens don't carry any syntactic function.
In our annotation, there are five \yicomment{six} types of non-syntactic tokens: 
sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
truncated words \yicomment{and retweet at-mentions}.\footnote{The tweets we analyze have at most 140
  characters. Although Twitter has doubled the tweet length limit to
  280 characters since our analysis, we believe this type of token
  will still remain.}  Figure \ref{fig:non-syn-toks} illustrates examples of
these non-syntactic tokens.  As discussed above, these are generally
tagged with the \emph{other} (\texttt{X}) part of speech, except
emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
7.5\% \yicomment{should change according to tab1} of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.

@@

Inspired by the way UD deals with \emph{punctuation} (which is
canonically non-syntactic), we adopt the following
conventions:\yicomment{shall we mention how we segment sentences? Seems relevant here}
\begin{itemize}
\item If a non-syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate;
\item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
%\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
\item Non-syntactic tokens are mostly labeled as {\it discourse}, but
  URLs are always labeled as {\it list}, following the UD\_English dataset.
\\ \yicomment{For retweet at-mention case, we attach the retweet at-mentions to the RT sign, so that the retweet action and the people whose tweet is being retweeted could be connected.\footnote{We can also follow the first convention to attach the retweet at-mention to its predicate, but we think it is better for downstream tasks.}}
\end{itemize}

@@

\newcite{kong-EtAl:2014:EMNLP2014} proposed an additional
preprocessing step, \emph{token selection}, in their annotation process.
They required the annotators to first select the non-syntactic
tokens and exclude them from the final dependencies annotation.
%  \nascomment{confusing.  were they removed or
%  just labeled as non-syntactic and then excluded from the tree?  I
%  think they were not actually removed, and were still available,
%  e.g., for defining features of the input for parsing}
In order to keep our annotation conventions in line with UD norms \yicomment{and preserve the original tweets as much as possible},
we include non-syntactic tokens in our annotation following the
conventions above. Compared with \citet{kong-EtAl:2014:EMNLP2014},
we also gave a clear\yicomment{much clearer} definition of non-syntactic tokens, which helped
us avoid confusion during annotation.

@@

\subsubsection{Annotation Process}
Our annotation process was conducted in three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the \yicomment{general} UD
annotation conventions and our guidelines \yicomment{specifically for annotating tweets}.
Both the guidelines and annotations
were further refined by the authors of this paper to increase
the coverage of our guidelines and solve inconsistencies between
different annotators during this exercise. In the second stage, a POS tagger and
parser were trained on the annotated data from the first stage (1,050\yicomment{changed to 1050} tweets in total),
and \yicomment{were?}used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data. Finally, an extra
layer of word-level normalization\yicomment{see 10 th col of conllu data, also mention we could recover the original tweets also from this col (tokenization)} was manually annotated for data
analysis purposes.\yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them. Good story :)}

@@

We report the inter-annotator agreement between the annotators
in the second stage\yicomment{tokenization is easier, did not do inter-annotator agreement}. The agreement on POS is 96.6\%, the unlabeled
dependency agreement is 88.8\% and the labeled dependency agreement
is 84.3\%. Further analysis shows the major disagreements on POS
involve entity names (30.6\%) \yicomment{noun phrases or proper noun phrases, do we need example here?} and topical hashtags (18.1\%).
Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' \yicomment{need to relate to previous error analysis, entity names maybe?}can
be understood as a verbal phrase but also as the name of the Coldplay's
single and tagged as proper noun. \yicomment{need to say the reason why dependency inter-annotator agreement is low? 1. POS disagreement lead to big difference in understanding the semantics. 2. Some special constructions like ellipsis lead to different view of tweets. Fig3 is an example of 2.}An example of a disagreement on
dependencies is shown in Figure \ref{fig:disagree}.  Depending on
whether this is an example of an empty auxiliary verb, or a clause-modified
noun, either annotation is plausible.

>>>>

\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$#1]}}
\newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
\newcommand{\yicomment}[1]{\textcolor{gray}{[#1 ---\textsc{Yi}]}}
%\newcommand{\yjcomment}[1]{}
%\newcommand{\nascomment}[1]{}
%\newcommand{\yicomment}[1]{}

@@

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Using the extended guidelines \yicomment{including tokenization, POS tagging and parsing? (need to mention the annotation process/pipeline system not only consists parsing in abstract)}, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
labeled attachments. 
It is more than four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreement
among our annotations and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Using the new treebank,
we build a pipeline system to parse raw tweets into UD. To overcome the
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 transition-based parsers into a single one. Our
parser achieves an improvement of 2.6 in LAS over \nascomment{which
  comparison is this?}\yjcomment{my bad, it was fixed.} the baseline
and outperforms parsers that are state-of-the-art on other treebanks in both accuracy and speed.
\end{abstract}

@@

Based on these annotations, we designed a pipeline to parse 
raw tweets into universal dependencies. Our pipeline includes: a
bidirectional LSTM (bi-LSTM) tokenizer, a word cluster-enhanced POS
tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT}, and a stack LSTM parser
with character-based word representations
\cite{ballesteros-dyer-smith:2015:EMNLP}, which we refer to as our
``baseline'' parser.
To overcome the noise in our annotated data and achieve better performance
without sacrificing computational efficiency, we 
distill a 20-parser ensemble into a single greedy  parser 
\cite{DBLP:journals/corr/HintonVD15}.
We show further  that learning directly from the exploration of the ensemble parser
is more beneficial than learning from the gold standard ``oracle''
transition sequence. Experimental results show that an improvement of more
than 2.6 points \nascomment{again, not sure what this is quoting}\yjcomment{fixed} in LAS over the
baseline parser can be achieved with our distillation method and it outperforms
other state-of-the-art parsers in both accuracy and running speed.

The contributions of this paper include:
\begin{itemize}
\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
and created a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech tagging, and labeled universal dependencies annotation.
We also characterize the difficulties of creating such annotation.

@@

Kong et al.'s rapid, small-scale annotation effort was heavily constrained.  It was
carried out mostly by nonnative speakers \yicomment{should not emphasize non-native speakers (v2 also built by non-native speakers), but emphasize annotators with only cursory training, no clear annotation guidelines, no consensus/agreement on controversial cases, allow annotators to underspecify part of the tree and allow multiple different trees for the same tweets}, in a very short amount of
time (a day).  Driven both by the style of the text they sought to annotate
and by exigency, some of their annotation conventions included:
\begin{itemize}
\item Allowing an annotator to exclude tokens from the dependency
  tree.  A clear criterion for exclusion was not given, but many
  tokens were excluded because they were deemed ``non-syntactic''.
\item Allowing an annotator to merge a multiword expression into a
  single node in the dependency tree, with no internal structure.
  Annotators were allowed to take the same step with noun phrases.
\item Allowing multiple roots, since a single tweet might contain more
  than one sentence.
\end{itemize}
These conventions were justified on the grounds of making the
annotation easier for non-experts, but they must be revisited in our
effort to apply UD to tweets.

@@

%In Fig.~\ref{ex1}, {\tt RT} {\tt @yijialiu}, {\tt \#ACL2017}, {\tt http://url} and {\tt th} are all tagged as X and {\tt :)} is tagged as SYM. 
%{\tt rn} is tagged as ADV.
%We should note that multiple tokens are actually included in a phrasal abbreviation, and we use one of their tags as the tag of the whole abbreviation according to their dependency relation or semantic priority.
%aIf there is a hierarchy in the abbreviation, we use the tag of the head word. In UD, ``Right'' is the dependent of ``now '' in the dependency of {\tt rn}, so we tag {\tt rn} as ADV. 
%Although there is no head word in {\tt im}, we think that the subject is usually more informative than the tense in many downstream tasks such as semantic role labelling, so we use the tag of ``I'', e.g. PROPN as the tag of {\tt im}.  
%In Fig.~\ref{ex2}, {\tt RT} and {\tt $\heart$} would be tagged as VERB, {\tt http://url} as X, {\tt \#Awesome} as ADJ, {\tt \#NAACL}, {\tt @zypandora} and {\tt @nlpnoah} as PROPN. One exception is that we tag URLs always as X regardless whether they are syntactic tokens. The reason is that we observed, in UD\_English, that the URLs are all tagged as X and we want to conform with the UD dataset, although we think it is not appropriate and should be changed to tags such as PROPN when they are treated as syntactic tokens.

Compared to the effort of
\newcite{gimpel-EtAl:2011:ACL-HLT2011}, our approach simplifies some
matters.  For example, if a token is not considered syntactic by UD
conventions, it gets an \emph{other} (\texttt{X}) tag (Gimpel et
al.~had more extensive conventions).  Other phenomena, like
abbreviations, are more complicated for us, as discussed above;
Gimpel et al.~used a single part of speech for such expressions.

@@

Another important difference follows from the difference in
tokenization.  As discussed in \S\ref{sec:tok-anno}, UD calls for more
aggressive tokenization than that of \citet{ICWSM101540} which opted
out of tokenizing contractions and possessives and it was used by 
\citet{gimpel-EtAl:2011:ACL-HLT2011}. As a consequence, 
Gimpel et al. introduced new parts of speech for these cases
instead.\footnote{These tags only account for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

@@

\paragraph{Non-syntactic tokens.}  
\begin{table}
\centering
\begin{tabular}{lrr}
\multicolumn{2}{r}{syntactic (\%)} & non-syntactic (\%)\\ \hline
emoticons & 0.25 & 0.95 \\
RT & 0.14 & 2.49\\
hashtag & 1.02 & 1.24 \\
URL & 0.67 & 2.38 \\
truncated words & 0.00 & 0.49 \\
 \hline
 total & 2.08 & 7.55 \\
\end{tabular}
\caption{Proportions of non-syntactic tokens in our annotation. %\yicomment{should add also retweet at-mentions}
These statistics are obtained on 140 character-limited tweets. \label{tbl:non-synt-prop}}
\end{table}

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& \textcolor{orange}{\bf @coldplay} \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \& \tiny ADJ \& \tiny X \& \tiny PUNCT \\
		\end{deptext}
		\deproot{1}{root}
		\depedge[edge unit distance=1em]{1}{2}{discourse}
		\deproot{6}{root}
		\depedge[edge unit distance=1em]{6}{3}{discourse}
		\depedge[edge unit distance=1em]{3}{4}{discourse}
		\depedge[edge unit distance=1em]{3}{5}{punct}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.8em]{6}{10}{obl}
		\depedge[edge unit distance=1em]{10}{8}{case}
		\depedge[edge unit distance=1em]{10}{9}{det}
		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
		\depedge[edge unit distance=0.8em]{6}{12}{list}
		\deproot{13}{root}		
		\depedge[edge unit distance=0.8em]{13}{14}{discourse}
		\depedge[edge unit distance=0.8em]{13}{15}{punct}
	\end{dependency}
	\caption{An example tweet that contains non-syntactic tokens:
		\textcolor{red}{sentiment emoticon},
		\textcolor{orange}{retweet marker and its following at-mention},
		\textcolor{gray}{topical hashtag},
		\textcolor{blue}{referential URL}, and
		\textcolor{cyan}{truncated word}.
		This example tweet is a concatenation of three real tweets.
	}\label{fig:non-syn-toks}
\end{figure*}

@@

The major characteristic that distinguishes tweets from standard texts is that
a large proportion of tokens don't carry any syntactic function.
In our annotation, there are five types of non-syntactic tokens: 
sentiment emoticons, retweet markers and their following at-mentions, topical hashtags, referential URLs, and
truncated words.\footnote{The tweets we analyze have at most 140
  characters. Although Twitter has doubled the tweet length limit to
  280 characters since our analysis, we believe this type of token
  will still remain.}  Figure \ref{fig:non-syn-toks} illustrates examples of
these non-syntactic tokens.  As discussed above, these are generally
tagged with the \emph{other} (\texttt{X}) part of speech, except
emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
7.55\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
\yjcomment{I've merged retweet marker and retweet at-mention into one.}

@@

Inspired by the way UD deals with \emph{punctuation} (which is
canonically non-syntactic), we adopt the following
conventions:\yicomment{shall we mention how we segment sentences? Seems relevant here}

\begin{itemize}
\item For the at-mentions in retweet constructions, we attach them to their retweet markers. We will discuss our choice in the following paragraph;
\item For the rest non-syntactic tokens, if one token is within a sentence that has a clear predicate, it will be attached to this predicate. If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
%\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
\item Non-syntactic tokens are mostly labeled as {\it discourse}, but
  URLs are always labeled as {\it list}, following the UD\_English dataset.
%\\ \yicomment{For retweet at-mention case, we attach the retweet at-mentions to the RT sign, so that the retweet action and the people whose tweet is being retweeted could be connected.\footnote{We can also follow the first convention to attach the retweet at-mention to its predicate, but we think it is better for downstream tasks.}}
\end{itemize}

@@

\newcite{kong-EtAl:2014:EMNLP2014} proposed an additional
preprocessing step, \emph{token selection}, in their annotation process.
They required the annotators to first select the non-syntactic
tokens and exclude them from the final dependencies annotation.
%  \nascomment{confusing.  were they removed or
%  just labeled as non-syntactic and then excluded from the tree?  I
%  think they were not actually removed, and were still available,
%  e.g., for defining features of the input for parsing}
In order to keep our annotation conventions in line with UD norms \yicomment{and preserve the original tweets as much as possible},
we include non-syntactic tokens in our annotation following the
conventions above. Compared with \citet{kong-EtAl:2014:EMNLP2014},
we also gave a clear %\yicomment{much clearer}
definition of non-syntactic tokens, which helped
us avoid confusion during annotation.

@@

\subsubsection{Annotation Process}
Our annotation process was conducted in three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the \yicomment{general} UD
annotation conventions and our guidelines \yicomment{specifically for annotating tweets}.
Both the guidelines and annotations
were further refined by the authors of this paper to increase
the coverage of our guidelines and solve inconsistencies between
different annotators during this exercise. In the second stage, a tokenizer, a POS tagger, and
parser were trained on the annotated data from the first stage (1,050 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data. Finally, an extra
layer of word-level normalization\yicomment{see 10 th col of conllu data, also mention we could recover the original tweets also from this col (tokenization)} was manually annotated for data
analysis purposes. For example, ``idc'' is annotated as
`I\_don't\_care' and `4 my FAM' is as `for my familiy'.
Such normalization doesn't change our tokenization annotation. \yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them. Good story :)}\yjcomment{add ``a tokenizer''}

@@

We report the inter-annotator agreement between the annotators
in the second stage. There is few disagreement on the tokenization annotation.
The agreement on POS is 96.6\%, the unlabeled
dependency agreement is 88.8\% and the labeled dependency agreement
is 84.3\%. Further analysis shows the major disagreements on POS
involve entity names (30.6\%) \yicomment{noun phrases or proper noun phrases, do we need example here?}\yjcomment{i wasn't counting PROPN and NOUN confusion, but any type of confusion related with PROPN} and topical hashtags (18.1\%).
Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' \yicomment{need to relate to previous error analysis, entity names maybe?}can
be understood as a verbal phrase but also as the name of the Coldplay's
single and tagged as proper noun. \yicomment{need to say the reason why dependency inter-annotator agreement is low? 1. POS disagreement lead to big difference in understanding the semantics. 2. Some special constructions like ellipsis lead to different view of tweets. Fig3 is an example of 2.}An example of a disagreement on
dependencies is shown in Figure \ref{fig:disagree}.  Depending on
whether this is an example of an empty auxiliary verb, or a clause-modified
noun, either annotation is plausible.
